### 2017-04-04 paper/evaluation.tex
added placeholders from rq3

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default (see
Section~\ref{sec:rqC-1}), and compared their time cost with sequential
execution. We are interested in measuring the execution speedup (if
any) when the parallelization settings are activated.

%% To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
%% parallelization settings enabled by default identified in \numRQC{}
%% and compared their time cost with sequential execution. We are
%% interested in measuring the execution speedup (if any) when the
%% parallelization settings are activated. It is important to mention
%% that we ignored the remaining \Fix{??} subjects identified in
%% Section~\ref{sec:rqC-2} because it would be impractical to execute
%% each subject on specific conditions to measure the impact of
%% parallelization.

To enforce sequential execution, we analyzed the \numProjectsPar{}
subjects looking for the parallelism configuration inside the \pomf{} 
of each module. To run the subjects sequentially, we manually modified 
the Maven Surefire configuration in order to force the subjects to
execute tests in sequential mode.

>>>>

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default (see
Section~\ref{sec:rqC-1}). To measure the overall speedup obtained from
parallel execution, we compared the elapsed time in the default
execution (parallelization enabled) and re-executed the tests
sequentially.
To enforce sequential execution,
\Fix{elaborar metodologia}
\Fix{dizer que verificamos que a execucao eh consistente e o
outcome eh igual ao da execucao padrao}.
